Nock for Everyday Coders

### 2025-08-28 mss.tex
Post

The pseudocode has four nested `*[subject formula]`s, so I'm going to unwrap those to the bottom, and then build it up again. The layers are, in order:

@@

If we just did \lstinline[style=inlinecode]{*[a @2@ c [@0@ b]]}, then \lstinline[style=inlinecode]{[@0@ b]} would try to look up the \lstinline[style=inlinecode]{b} memory slot in \lstinline[style=inlinecode]{a}, NOT \lstinline[style=inlinecode]{*[a c]}. So \lstinline[style=inlinecode]{@9@} gives us one extra step to set up the core itself.

@@

Before explaining \lstinline[style=inlinecode]{@10@}, we need to introduce a new operator, \lstinline[style=inlinecode]{#}. \lstinline[style=inlinecode]{#} is the ``edit" operator. It has the form

>>>>

The pseudocode has four nested \lstinline[style=inlinecode]{*[subject formula]}s, so I'm going to unwrap those to the bottom, and then build it up again. The layers are, in order:

@@

If we just did \lstinline[style=inlinecode]{*[a @2@ c [@0@ b]]}, then \lstinline[style=inlinecode]{[@0@ b]} would try to look up the \lstinline[style=inlinecode]{b} memory slot in \lstinline[style=inlinecode]{a}, \textsc{not} \lstinline[style=inlinecode]{*[a c]}. So \lstinline[style=inlinecode]{@9@} gives us one extra step to set up the core itself.

@@

Before explaining \lstinline[style=inlinecode]{@10@}, we need to introduce a new operator, \lstinline[style=inlinecode]{#} hax. \lstinline[style=inlinecode]{#} hax is the ``edit" operator. It has the form
